Mapping Microblog Posts to Encyclopedia Articles

### 2011-03-03 lids/twittersearchwrap/paper/paper.tex

\begin{abstract}
Search results on Twitter are hard to analyze and read. To facilitate understanding the meaning of a search term in the context of Twitter, we have developed a system which annotates search results with entities that best describe the search result, thus offering a means of quickly grasping the meaning of the search results and at the same time providing starting points for further exploration of the search results' context. In an evaluation we show that the entities used for annotation represent the tweet's content in a suitable manner and that the annotations remain stable over time, i.e. when executing the same search at different times, the same entities are returned.
\end{abstract}

>>>>

\begin{abstract}
To facilitate understanding the meaning of a hash tag in the context of Twitter, we have developed a system which annotates hash tags based on Twitter search results with encyclopedia entities that best describe the hash tag, thus offering means of quickly grasping the meaning of the hash tag and at the same time providing starting points for further exploration of the hash tags' context. In an evaluation we show that the encyclopedia entities used for annotation represent the content in a suitable manner and that the annotations remain stable over time, i.e. when executing the same search at different times, the same entities are returned.
\end{abstract}
